Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-02-17 paper/1_Initial/manuscript.qmd
minor

One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception]. **TODO: ANA check if the definitions are correct**.
A recent systematic review suggested that various questionnaires [**WHICH ONES**] designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).

>>>>

<!-- 
Garfinkel - sensibility-> Self-perceived dispositional tendency to be internally self-focused and interoceptively cognisant,
Khalsa - sensibility -> Self-perceived tendency to focus on interoceptive stimuli (trait measure)
 -->

**todo**: reframe paragraph to reflect that review focus on looking at whether the self-report scales and interoceptive sensibility, which are both assessed with questionnaires tap onto a common or different construct

One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception]. 
A recent systematic review suggested that various questionnaires (e.g., MAIA, Body Perception Questionnaire, Body Awareness Questionnaire, Eating Disorder Inventory) designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
